>

### 2025-12-10 docs/exec-summary/_seasonality.qmd
Draft an initial report using Elsevier template
Revise the manuscript to address all of the reviewers' comments

### Exploring seasonality in the dataset

Exploration on seasonality was done on detrended daily, weekly, and monthly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF). Seasonal plots were generated for weekly and yearly pattern by using daily and monthly data, respectively.  To generate the seasonal plots, the data was first deconstructed based on its period. For daily data, the weekly period was used; while for monthly data, the yearly period was used. The weekly period was obtained by creating an ordered value formatted as year - week, e.g. `2018 - W01`. Similarly, monthly period was obtained by creating an ordered value formatted as year - month, e.g. `2018 - M01`. We then grouped the series by its deconstructed period and visually examine seasonality as overlapping pattern in most periods. To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.

>>>>

::: {.content-visible unless-meta="in.article"}
### Exploring seasonality in the dataset
:::

Exploration on seasonality was done on detrended daily and weekly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF). Seasonal plots were generated for weekly and yearly pattern by using daily and weekly data, respectively.  To generate the seasonal plots, the data was first deconstructed based on its period. For daily data, the weekly period was used; while for weekly data, the yearly period was used. The weekly period was obtained by creating an ordered value formatted as year - week, e.g. `2018 - W01`. Similarly, monthly period was obtained by creating an ordered value formatted as year - month, e.g. `2018 - M01`. We then grouped the series by its deconstructed period and visually examine seasonality as overlapping pattern in most periods. To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.

### 2025-12-10 docs/exec-summary/_source-data.qmd
Revise the manuscript to address all of the reviewers' comments

All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription data since 1994 which still grows expansively. The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023. All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013]. The database offers a longitudinal record, where each individual has a uniquely anonymized tracking identifier. All records contain fields on the date of medication dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code. Except for the over the counter drugs and medication dispensed during hospitalization, all medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.

This analysis includes daily drug administration from a static cohort of adults aged 18 to 65 years and prescribed anxiolytics or antidepressants at least once in the period 2018-2022.

>>>>

All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription records since 1994. The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^ of September 2023. In the Netherlands, the primary route of obtaining prescription medications is through community pharmacies, as physicians issue prescriptions that are almost exclusively dispensed in these settings. Consequently, the database provides a comprehensive longitudinal record for each individual, supported by high patient-pharmacy commitment. All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013]. Each record includes the dispensing date, quantity, dose regimen, number of days prescribed, prescribing physician, and the corresponding Anatomical Therapeutic Chemical (ATC) code. Medication dispensed during hospitalization and over-the-counter drugs are not captured, but prescription medication records in community pharmacies are otherwise complete.

This analysis includes daily drug administration from a static cohort of adults aged 18 to 65 years and prescribed anxiolytics or antidepressants at least once in the period 2018-2022. For this study, only a subset of the database was used to construct the DPN: anonymized patient identifiers, age, prescription start and end dates, and ATC codes. No additional individual-level data were included to align with internal research data management regulations. Other demographic or clinical information available in the database was not extracted.
